Identifying Departures from the Fully Developed Speckle Hypothesis in Intensity SAR Data with Non-Parametric Estimation of the Entropy

### 2023-12-10 Text/Articles/MIGARS_2024/R1-The Entropy as a Proxy for Fully Developed Speckle.Rmd
improved code

# Number of replications
R <- 10

@@

```{r Table_gama_sar12, echo=FALSE, message=FALSE, warning=FALSE, results='asis'}

set.seed(1234567890, kind = "Mersenne-Twister")

sample_sizes <- c( 9, 25, 49, 81, 121)
R <- 100
mu <- 5
L <- 2
alpha <- -1000

true_entropy <- entropy_gamma_sar(L, mu)

generate_samples <- function(sample_size, replication, mu, alpha, L) {
  samples <- vector("list", replication)
  for (r in 1:replication) {
    samples[[r]] <- gi0_sample(mu, alpha, L, sample_size)#
  }
  return(samples)
}

calculate_entropy_and_test_table <- function(sample_sizes, R, mu, alpha, L) {
  estimators <- list(
    #" " = bootstrap_vasicek_estimator,
    "$\\widetilde{H}_{C}$ " = bootstrap_correa_estimator,
    "$\\widetilde{H}_{E}$ " = bootstrap_ebrahimi_estimator,
    "$\\widetilde{H}_{AO}$ " = bootstrap_al_omari_1_estimator
  )

#   estimators <- list(
#   "Correa Bootstrap" = bootstrap_correa_estimator,
#   "Ebrahimi Bootstrap" = bootstrap_ebrahimi_estimator,
#   "Al Omari Bootstrap" = bootstrap_al_omari_1_estimator
# )

  output <- data.frame(
    SampleSize = integer(0),
    Estimator = character(0),
    MeanEntropy = numeric(0),
    ZStatistic = numeric(0),
    PValue = numeric(0)
  )

  for (ssize in sample_sizes) {
    samples <- generate_samples(ssize, R, mu, alpha, L)

    for (estimator_name in names(estimators)) {
      estimator <- estimators[[estimator_name]]
      v.entropy <- numeric(R)

      for (r in 1:R) {
        sample <- samples[[r]]

        if (grepl(" ", estimator_name)) {
          v.entropy[r] <- estimator(sample, B = 100)
        } else {
          v.entropy[r] <- estimator(sample)
        }
      }

      mean_entropy <- mean(v.entropy)

      z_statistic <- sqrt(R) * (mean_entropy - true_entropy) / sd(v.entropy)
      p_value <- 2 * (1 - pnorm(abs(z_statistic)))

      output <- rbind(
        output,
        data.frame(
          SampleSize = ssize,
          Estimator = estimator_name,
          MeanEntropy = round(mean_entropy, 5),
          ZStatistic = round(z_statistic, 5),
          PValue = round(p_value, 5)
        )
      )
    }
  }

  colnames(output) <- c("$n$", "Estimator", "Mean Entropy", "$Z$ Statistic", "$p$ Value")

  table_result <- kbl(
    output,
    caption = "Hypothesis Testing for $G_I^0$, $\\mu=5$, $L=2$, $\\alpha=-1000$ , $H_{\\Gamma_{\\text{SAR}}}=2.493$.",
    format = "latex",
    booktabs = TRUE,
    align = "c",
    escape = FALSE,
    digits = 4,
    label = "table_hipotesis"
  ) %>%
    #add_header_above(c(" ", " ", "Estimador" = 1, " ", " ")) %>%
    collapse_rows(columns = 1:3,latex_hline = "major", valign = "middle") # %>%
    #kable_styling(latex_options = c("striped"))

  return(table_result)
}

result_table <- calculate_entropy_and_test_table(sample_sizes, R, mu, alpha, L)
print(result_table)

>>>>

# Number of replications
R <- 100

@@

```{r Simulated_data_test_gi0, echo=FALSE, message=FALSE}

# Number of replications
R <- 100

# Number of bootstrap replications
B <- 10
mu_values <- c(5)
alpha <- -1000
L <- 2

  estimators <- list(
    #" " = bootstrap_vasicek_estimator,
    "$\\widetilde{H}_{C}$ " = bootstrap_correa_estimator,
    "$\\widetilde{H}_{E}$ " = bootstrap_ebrahimi_estimator,
    "$\\widetilde{H}_{AO}$ " = bootstrap_al_omari_1_estimator
  )

calculate_results_test_gi0 <- function(sample_sizes, R, B, mu_values, alpha, L, estimators) {
  results_list <- list()

    results <- calculate_entropy_and_test(sample_sizes, R, B, mu_val, alpha, L, estimators)
    df <- as.data.frame(results)

results_gi0_1 <- calculate_results_test_gi0(sample_sizes, R, B, mu_values, alpha, L, estimators)

save(results_gi0_1, file = "./Data/results_gi0_1.Rdata")

```{r Table_test_gi0, echo=FALSE, message=FALSE, warning=FALSE, results='asis'}

load("./Data/results_gi0_1.Rdata")

for (mu_val in mu_values) {
  results_data <- results_gi0_1[[as.character(mu_val)]]

  table_result <- kbl(
    results_data,
    caption = paste("Hypothesis Testing for $G_I^0$, $\\mu =", mu_val, "$, $L=2$, $\\alpha=-1000$ , $H_{\\Gamma_{\\text{SAR}}}=2.493$."),
    format = "latex",
    booktabs = TRUE,
    align = "c",
    escape = FALSE,
    digits = 4,
    label = "table_hipotesis"
    #label = paste("table_hipotesis", mu_val, sep = "")
  ) %>%
    collapse_rows(columns = 1:3, latex_hline = "major", valign = "middle")

  print(table_result)
}
